Figure 1.Luminal Study Groups

### 2022-01-06 reports/rmarkdown/manuscript/Figure1.Rmd
Adding BV and HIV colour coding

---
title: "Figure 1.Luminal Patient Grouping"
output: 
  pdf_document:
    fig_caption: yes
    keep_tex: yes
header-includes: 
- \usepackage{float}
editor_options: 
  chunk_output_type: console
---

@@

  o <- order( rowSums(temp_legend) , decreasing = T)
  sample_o <- names(group_annotation)[ order( group_annotation )]
  temp <- temp[o,sample_o]*100
  temp <- rbind(temp[1:16,], Other = colSums(temp[17:nrow(temp),]) )

@@

}

@@

# Bacterial Communities
bac_communities <- bac_communities %>% 
  rownames_to_column(var = "Taxa") %>%
  mutate("bacterial communities"= factor(paste0("BC",sprintf("%02d",bac_communities$x)))) %>%
  select(-x)

>>>>

---
title: "Figure 1.Luminal Study Groups"
output: 
  pdf_document:
    fig_caption: yes
    keep_tex: yes
header-includes: 
- \usepackage{float}
editor_options: 
  chunk_output_type: console
---

@@

  o <- order( rowSums(temp) , decreasing = T)
  sample_o <- names(group_annotation)[ order( group_annotation )]
  temp <- temp[o,sample_o]*100
  temp <- rbind(temp[1:16,], Other = colSums(temp[17:nrow(temp),]) )

@@

  l <- c("BV:","Normal","Intermediate","BV")
  legend(x = 10, y = 111, #"bottom", inset = c(0, -0.5),
         bty = "n", horiz=TRUE, cex=0.7, xpd = T, 
         border = "white", 
         legend = l, x.intersp=0.5, xjust=0,
         text.width = c(0, map_dbl(l, ~strwidth(.x)/2)) ,
         fill=c(NA, "#d7d7d7","orange","tomato"))
  l2 <- c("HIV:","HIV-","HIV+")
  legend(x = 80, y = 111, # bottom position: par("usr")[3]-5
         bty = "n", horiz=TRUE, cex=0.7, xpd = T,
         border = "white",
         legend = l2, x.intersp=0.5, 
         text.width =c(0, map_dbl(l2, ~strwidth(.x)/2)),
         fill=c(NA, "#d7d7d7", "tomato"))
}

@@

# Bacterial Communities
bac_communities <- bac_communities %>% 
  rownames_to_column(var = "Taxa") %>%
  mutate("bacterial communities"= factor(paste0("BC",sprintf("%02d",bac_communities$x)))) %>%
  select(-x) %>%
  arrange(`bacterial communities`)
